---
title: "Data preparation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(lubridate)
library(dygraphs)
library(dutils)
library(ggplot2)
library(purrr)
library(flextools)
library(evsim)
```


This notebook aims to prepare the energy data sets that will be used in the next notebooks where smart charging will be applied using `flextools` package. This second part of the course aims to use custom data sets for all exercises, so below there's the code that pretends to read the data sets.

# Simulation definition

We will apply smart charging over charging sessions that occur in a certain environment, for example a building. Select a building that could be an interesting study case to analyse a charging hub on it. Define the characteristics of the building:

- Where is it located?
- Number of floors
- Is it a residential or office building?
- Does it have charging points currently?
- Does it have solar panels?

Let's define now the simulation time characteristics:

- Year of the simulation
- Months of the simulation
- Time resolution of the simulation


Is there any other relevant information about our study case?

- 
- 


# Building data

Read the demand profiles from the selected building:

```{r}
# building_df <- 
```

Plot the time-series data frame:

```{r}

```

Is is possible that this building profile was recorded during a time period that does not coincide with the date-time sequence of our simulations. We can adapt the building's date-time sequence to the simulation year, using function `dutils::change_timeseries_year` (see function's help documentation for more details):

```{r}
# building_df <- change_timeseries_year(
#   df = building_df,
#   year_out = 
# )
```


# EV sessions simulation

To simulate smart charging, the first thing we need is a data set of charging sessions. Create a custom EV model for the study case of this project using `evsim` function `evsim::get_custom_ev_model`. Remember that you have to configure the parameters of your EV user profiles in a list of tibbles (argument `parameters_lst`). You can create this list manually in this notebook or by reading the multiple workseets of an Excel file (for that you can use functions `purrr::map()`, `readxl::excel_sheets()` and `readxl::read_excel()`):

```{r}
# ev_model <-
```


Create a custom EV charging sessions data set using `evsim` function `evsim::simulate_sessions()`. Choose the scenario you want to simulate, but a high-demand scenario is advised to better assess the impact of EV charging and the potential benefits of smart charging. Describe the corresponding chosen scenario.

```{r}
# set.seed(1234)
# ev_sessions <- 
```


Get the time-series EV demand **of every charging session** using `evsim` function `evsim::get_demand()`.

```{r}
# ev_demand <-
```


Plot the time-series EV demand of the simulated charging sessions using `evsim` function `evsim::plot_ts()`.

```{r}

```


Plot now the aggregated EV demand. There are two different ways to do it:

* Directly in the plot, stacking the curves:
```{r}

```

* Sum all EV users first, and then plot:
```{r}

```


Answer the following questions:

* Is there any **peak hour** when most of EV users are consuming?
* Which is the maximum demand?
* Which is the average peak?
* Which is the user profile that mostly contributes to the peak?


# Solar PV Production

It is usual to use smart charging with the objective to maximize the use of renewable energies. We can simulate this strategy with flextools, so if there's a solar PV installation in the building's roof or neighbourhood, read the corresponding time-series profile:

```{r}
# production_df <-
```

Adapt the the year of the time-series data frame if it is not the simulation year:

```{r}
# production_df <- change_timeseries_year(
#   df = production_df,
#   year_out = 
# )
```



# Energy prices

Another usual objective of smart charging is to minimize the energy cost. For that purpose, we need energy tariffs and price information. Create a time-series data frame with energy prices that contains the columns `price_imported` and `price_exported`, and (if available) also the imbalance market prices `price_turn_up` and `price_turn_down`:

```{r}
# prices_df <-
```

Adapt the the year of the time-series data frame if it is not the simulation year:

```{r}
# prices_df <- change_timeseries_year(
#   df = prices_df,
#   year_out = 
# )
```


# All together

Join all the variables in the same data frame `energy_df` to be used in the following exercises. The `energy_df` data frame should contain the following columns:

- `datetime`: date-time sequence of the simulation
- `building`: power demand from the `building_df`
- `evs`: aggregated power demand from the different user profiles in `ev_demand`
- `solar`: power production from solar PV installation in `production_df`
- `price_imported`: imported energy price from `prices_df`
- `price_exported`: exported energy price from `prices_df`
- `price_turn_up`: imbalance market price to turn energy demand up, from `prices_df` (if available)
- `price_turn_down`: imbalance market price to turn energy demand down, from `prices_df` (if available)

If some variables are not available from your study case you can use the example values from the `energy_profiles` data frame provided by `flextools`.


```{r}
# energy_df <- 
```


Finally, save the environment in a file:

```{r}
# save.image(file = "data.RData")
```



