---
title: "Smart charging for grid congestion"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(lubridate)
library(dygraphs)
library(dutils)
library(ggplot2)
library(purrr)
library(flextools)
library(evsim)
```


This notebook aims to simulate smart charging in a scenario where the EV load causes grid congestion. Before running into the exercises make sure that you have already simulated the EV charging sessions (`ev_sessions`) in the `1_data.Rmd` notebook.


# Grid capacity

Imagine that we have to charge these EVs in an installation that has a specific **grid connection that can't be increased**. Set the maximum grid capacity to the 50% of your peak:

```{r}
# grid_capacity <- 
```


To configure this grid capacity in the `smart_charging()` function, a column with the same name than the EV user profile in the `sessions` parameter must be found in the `opt_data` parameter. 

First, let's assume that all sessions will be coordinated as the same user profile. For that, let's `mutate` the `ev_sessions` object to assign the value `"EV"` to the column `Profile`:

```{r}
sessions <- ev_sessions %>%
  mutate(Profile = "EV")
```

Second, add the corresponding column to the `opt_data` object as a setpoint:

```{r}
opt_data <- tibble(
  datetime = ev_demand$datetime, # Same date-time sequence than the demand
  EV = grid_capacity
)
```

Now, you can test the `smart_charging()` function with different smart charging **methods**. 

* Postpone:

```{r}

```

* Interrupt:

```{r}

```

* Curtail:

```{r}

```


For each one:

1. Apply the `smart_charging()` function
2. Plot the time-series setpoint together with the EV demand from the coordinated sessions (use function `evsim::get_demand()`), to see if the maximum grid capacity can be respected


Which method seems to be more suitable for this EV demand?

## User profiles

From the different User profiles that we have, choose the one with more flexibility potential for peak shaving. Apply smart charging using only this user profile:

```{r}

```

Moreover, you can configure that only a part of the EV users of a specific profile respond to the smart charging signal, using the `responsive` parameter in `smart_charging()` function. Configure that only the 50% of the users of the selected EV user profiles accept to participate:

```{r}

```

Answer the following questions:

* Are the results still acceptable?
* Which percentage of responsiveness is the limit to avoid surpassing the grid capacity?



# Demand-response signals

As a Charging Point Operator (CPO) we could participate in a flexibiliy market, where the DSO can establish dynamic capacity signals according to the rest of loads in the power system.

From the object `energy_df` previously created, plot the EV demand on top of the building demand to see the total consumption of both loads:

```{r}

```

Simulate a daily flexibility market offer with the following specifications:

* Baseline: historic maximum peak demand
* Power request: turn-down demand 15 kW
* Time request: from 17:00 to 22:00

```{r}
# offer_df <- 
```

```{r}

```

Now simulate the same considering that the power request for turn-down demand is 30 kW:

```{r}

```

Is it possible to achieve? 

Now configure the parameter `energy_min = 0` to see the impact to the users in order to deliver the requested flexibility offer:

```{r}

```

Calculate the average percentage of energy charged for every user profile and day:

```{r}

```







